---
title: "Airbnb Price Distribution in Seattle"
author: "ningze zu"
date: "12/17/2018"
output:
  slidy_presentation: default
  ioslides_presentation: default
  beamer_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(ggplot2,knitr,arm,data.table,foreign,gridExtra,car,stringr,rstan,zoo)
library(tidyverse)
library(dplyr)
library(leaflet)
library(RColorBrewer)
library(corrplot)
library(ggcorrplot)
library(lattice)
library(plotly)
library(png)
library(scales)
library(graphics)
library(ggmap)
library(leaflet)
library(readr)
library(boot)
library(ggpubr)
library(benford.analysis)
library(BenfordTests)
#air <- read.csv("air.csv")
#airbnb_se <- air %>% dplyr::filter(state == "WA")
#airbnb_se$Area <- rep("Seattle",nrow(airbnb_se))
#sea <- read.csv("sea.csv")
#se <- sea %>% dplyr::filter(state == "WA")
#nei <- data.frame(se$neighbourhood_group_cleansed)
#airbnb_se$market <-NULL
#airbnb_se <- cbind(airbnb_se,nei)
#colnames(airbnb_se)[colnames(airbnb_se)=="se.neighbourhood_group_cleansed"] <- "neighbourhood"
airbnb_se <- read.csv("sea_airbnb.csv")
airbnb_se_m <- airbnb_se %>% filter(price > 0 & price <= 1000) 

```

## Abstract

In this project, I will use benford's law to analysis the distribution of Airbnb listings' price in Seattle and perform an exploratory data analysis figure out other features that are relevant to the rental price of Airbnb.


## Parts

- Price Distribution Benford's Law
- Benford's Law
- Other Features


## Airbnb Price Distribution 

```{r echo=FALSE,message=FALSE}
airbnb_se <- read.csv("sea_airbnb.csv")
airbnb_se_m <- airbnb_se %>% filter(price > 0 & price <= 1000) 
    ggplot(airbnb_se_m, aes(price, fill = room_type)) + 
      geom_histogram(binwidth = 10) + theme_classic() +   
      scale_fill_brewer(palette = "RdPu") + 
      scale_x_continuous(breaks = seq(0, 1000, by = 200)) + 
      xlab("\nPrice ($)") + ylab("Frequency of Price\n") + 
      ggtitle("Figure 1. Airbnb Price Distribution \n  in Seattle ($0 ~$1000)") + 
      theme(axis.title.x = element_text(face="bold",  size=14), 
            axis.title.y = element_text(face="bold",  size=14),
            plot.title = element_text(size=16, face="bold"),  
            axis.text.x  = element_text(vjust=0.5, size=12)) +
      theme(plot.title = element_text(hjust = 0.5)) 
```

## Benford's Law

```{r echo=FALSE,message=FALSE}
bf <- benford(airbnb_se_m$price)
plot(bf)
```

## Benford's Law

```{r echo=FALSE,message=FALSE}
bf
```


## Get Suspects

```{r}
getSuspects(bf, airbnb_se_m)
``` 


## Other Features (Bedrooms)

```{r  echo=FALSE,message=FALSE, warning=FALSE}
##bedroom ~ price 
airbnb_se_bed <- airbnb_se_m %>% filter(price > 0 & price <= 1000) %>% 
  filter(bedrooms < 15)
bedroom_se <- airbnb_se_bed %>% dplyr::select(price, bedrooms)
bedroom_se <- bedroom_se %>% group_by(bedrooms) %>% summarise(mean_price = mean(price))
#barplot
ggplot(bedroom_se, aes(y=mean_price, x=bedrooms,fill=as.factor(bedrooms))) + 
      geom_bar(stat="identity", fill="pink") +
      scale_x_continuous(name ="Number of Bedrooms", breaks = seq(0, 50, by = 5)) +   
      scale_y_continuous(name = "Mean price", breaks = seq(0, 1000, by = 200)) + theme_bw() + 
      ggtitle("Figure 2 Price over different number of bedrooms") +
      theme(axis.title.x = element_text(face="bold",  size=12), 
            axis.title.y = element_text(face="bold",  size=12),
            plot.title = element_text(size=14, face="bold")) +
      theme(plot.title = element_text(hjust = 0.5))
```


## Other Features (Accommodates)

```{r echo=FALSE,message=FALSE} 
 ggplot(airbnb_se_m, aes(x=accommodates, y=price)) + geom_point(color="pink") + 
      geom_smooth(method = "lm", color="green") + theme_bw() + 
      ggtitle("Figure 3 ~ accommodates")+  
      theme(axis.title.x = element_text(face="bold",  size=12), 
            axis.title.y = element_text(face="bold",  size=12),
            plot.title = element_text(size=14, face="bold")) +
      theme(plot.title = element_text(hjust = 0.5))
```

## Other Features (Room Type)

```{r echo=FALSE,message=FALSE, warning=FALSE}
#### pie chart ~ room type
airbnb_se_3 <- airbnb_se_m %>% filter(price > 0 & price <= 1000) %>% dplyr::select(room_type)
type_sea <- airbnb_se_3  %>% group_by(room_type) %>% 
  summarise(n=n()) 

colors <- c('pink', 'violet', 'salmon')

plot_ly(type_sea,  labels = ~room_type, values = ~n, type = 'pie',  textposition = 'inside',
        textinfo = 'label+percent',
        hoverinfo = 'text',
        marker = list(colors = colors,
                      line = list(color = '#FFFFFF')),
        showlegend = TRUE) %>%
  layout(title = 'Figure 4 Room Type Proportion',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
```

## Other Features (Room Type)

```{r echo=FALSE,message=FALSE, warning=FALSE}
#####
airbnb_se_2 <- airbnb_se_m %>% filter(price > 0 & price <= 1000) %>% dplyr::select(room_type, price)
type_se <- airbnb_se_2  %>% group_by(room_type) %>% 
  summarise(mean_price = mean(price)) %>% arrange(desc(mean_price))
ggplot(type_se, aes(y=mean_price, x=room_type, fill=room_type)) + 
      geom_bar(stat="identity") + scale_fill_brewer(palette = "RdPu") +
      scale_x_discrete(name ="Different Room Type") + 
      scale_y_continuous(name="price($)", breaks = seq(0, 1000, by = 50)) + 
      ggtitle("Figure 5 Price ~ Room type") + 
      theme_bw() +
      theme(axis.title.x = element_text(face="bold",  size=12), 
            axis.title.y = element_text(face="bold",  size=12),
            plot.title = element_text(size=14, face="bold"),  
            axis.text.x  = element_text(vjust=0.5, size=10)) +
      theme(plot.title = element_text(hjust = 0.5))
```



## Other Features (Neighbourhoods)

```{r  echo=FALSE,message=FALSE, warning=FALSE, fig.width=6, fig.height=4}
airbnb_se_nei <- airbnb_se_m %>% filter(price > 0 & price <= 1000) %>% dplyr::select(room_type, price,neighbourhood)
nei_se <- airbnb_se_nei %>% group_by(room_type,neighbourhood) %>% 
  summarise(mean_price = mean(price)) %>% arrange(desc(mean_price))



ggplot(data = nei_se, mapping = aes(x = room_type,y =neighbourhood, fill = mean_price)) + 
  geom_tile() + geom_text(aes(label = round(mean_price,0)), size=3)+ scale_fill_gradient(name = "Average Price",
                      low = "ivory",
                      high = "hotpink")  + xlab(label = "Room Type") + ylab(label = "Neighbourhood") +theme_classic()+ ggtitle("1. Neighbourhood ~ Room type")+ theme(axis.title.x = element_text(face="bold",  size=12), 
            axis.title.y = element_text(face="bold",  size=12),
            plot.title = element_text(size=14, face="bold")) +
      theme(plot.title = element_text(hjust = 0.5))
```


## Other Features (Neighbourhoods)

```{r echo=FALSE,message=FALSE, warning=FALSE, fig.width=6, fig.height=4}
####3
airbnb_se_be <- airbnb_se_m %>% filter(price > 0 & price <= 1000) %>% filter(bedrooms <= 10) %>% dplyr::select(bedrooms, price,neighbourhood)
bed_se <- airbnb_se_be %>% group_by(bedrooms,neighbourhood) %>% 
  summarise(mean_price = mean(price)) %>% arrange(desc(mean_price))

 
ggplot(data = bed_se, mapping = aes(x = bedrooms, y =neighbourhood, fill = mean_price)) + 
  geom_tile() + geom_text(aes(label = round(mean_price,0)), size=3)+ scale_fill_gradient(name = "Average Price",
                      low = "ivory",
                      high = "hotpink")  + xlab(label = "Number of bedroom") + ylab(label = "Neighbourhood") +theme_classic()+ ggtitle("2. Neighbourhood ~ Bedroom")+ theme(axis.title.x = element_text(face="bold",  size=12), 
            axis.title.y = element_text(face="bold",  size=12),
            plot.title = element_text(size=14, face="bold")) +
      theme(plot.title = element_text(hjust = 0.5))
```



